Model Search in Relational Domains

### 2016-10-19 learning.tex
conflict analysis

\section{Abstract Conflict Analysis}
A conflict analysis in a SAT solver can be seen as abductive 
reasoning where a singleton assignment $c$ is replaced by a partial 
assignment that is sufficient to infer $c$ \pscmt{???}.  Thus, a conflict 
analysis is a generalization of an under-approximation of a set of 
countermodels~\cite{sas12,dhk2013-popl}, where a countermodel is a 
set of structures that do not satisfy a formula \pscmt{this explanation does not help the reader, who will mix up counterexamples and countermodels}.  Since relational 
abstract domains have more complex structure than a partial 
assignments domain, so the lifting of {\em first-UIP} algorithm~\cite{uip} 
and clause learning to any arbitrary lattice structure is a non-trivial task.

>>>>

\section{Abstract Conflict Analysis}
A conflict analysis in a SAT solver can be seen as abductive 
reasoning which underapproximate a set of models that do not satisfy a 
formula~\cite{sas12,dhk2013-popl}.  
\Omit {
where a singleton assignment $c$ is replaced by a partial 
assignment that is sufficient to infer $c$.  Thus, a conflict 
analysis is a generalization of an under-approximation of a set of 
countermodels, where a countermodel is a 
set of structures that do not satisfy a formula 
}
Since relational abstract domains have more complex structure than a partial 
assignments domain or interval domain, so the generalization of {\em first-UIP} algorithm~\cite{uip} and clause learning in a relational lattice structure is non-trivial.
